Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Domain fronting.

Most of the discussion in this paper will use the specific example of the
Google frontend server as a front for App Engine.
App Engine is the system on which we have based our deployment,
and it suffices to illustrate the concept of domain fronting.
There are other systems, discussed in Section~\ref{sec:otherservices}
that can be substituted for App Engine, with few or no modifications.
When an example talks about ``App Engine,'' the reader may instead think
of other systems such as the CloudFlare content delivery network.

The confidentiality provided by HTTPS

Alternate domain fronting: use just an IP (no DNS and no SNI).

@@

\section{Deployment}

@@

\subsection{Other deployment scenarios}

>>>>

``Domain fronting'' is the term we use for one of the key techniques used by meek.
Domain fronting is the use of different domain names at different layers of the network stack.
In the DNS query and TLS server name indication (SNI)~\cite[Section~3]{rfc6066},
which are visible to the censor, one domain name (the ``front domain'') appears;
while in the HTTP Host header~\cite[Section~14.23]{rfc2616},
which is hidden from censor by HTTPS encryption,
a different name (the actual destination) appears.
Domain fronting works in systems that use the Host header in order to
multiplex many domain names behind one HTTPS frontend;
among these systems are Google's infrastructure and the
CloudFlare content delivery network.
Domain fronting can also work using only an IP address in place of
a front domain. In this case there is no DNS query and no SNI in the TLS layer,
but the actual destination still appears in the Host header.
Domain fronting has been used successfully for years by GoAgent~\cite{goagent}
(which uses a bare IP address without SNI)
and by one of the rendezvous methods of flash proxy~\cite{flashproxy}.
In the examples in this paper, the front domain is www.google.com
and the actual hidden destination domain is meek-reflect.appspot.com,
which is our custom web app that aids in circumvention.

For concreteness, and because it is what we have deployed so far,
the examples in this paper will use Google and App Engine as the specific
third-party web service used for circumvention.
Other systems that support domain fronting may be substituted for Google,
and other alternative deployments are discussed in Section~\ref{sec:otherdeployment}.

@@

\section{Deployment}
\label{sec:deployment}

@@

\subsection{Other deployment scenarios}
\label{sec:otherdeployment}
